Relationships in the extremes and their influence on competition and coexistence

### 2021-09-01 paper/Paper.Rnw
minor changes to comments

%Para on when delta=1 (annual species) - in this case, coexistence is only possible when mu1-mu2 is close to 0, and in that case the only
%thing allowing for coexistence at all is storage effects. Interetingly (and this is the topic sentence), "the rest" of storage effects are
%negative, and it's the ATA component of storage effects which are allowing the species to coexist. Suggests the possibility that for 
%annual species whcih are close competitors, ATAs might be especially important? Jasmin ought to check on this to make sure it's accurate.
%What I'm suspicious about is that for annual species which are close competitors (say, mu1-mu2=0), and in the symmetric case, storage
%effects in the lotery model actually don't opperate, and there is no coexistence. That sounds weird to me. Can we get some independent
%verification of that? Why would annual species be different in this respect? There must be some delta between 0.8 and 1 where \Delta^[EC]
%switches from positive to negative.

@@

>>>>

%***DAN: drop the delta =1 case from here
%Para on when delta=1 (annual species) - in this case, coexistence is only possible when mu1-mu2 is close to 0, and in that case the only
%thing allowing for coexistence at all is storage effects. Interetingly (and this is the topic sentence), "the rest" of storage effects are
%negative, and it's the ATA component of storage effects which are allowing the species to coexist. Suggests the possibility that for 
%annual species whcih are close competitors, ATAs might be especially important? Jasmin ought to check on this to make sure it's accurate.
%What I'm suspicious about is that for annual species which are close competitors (say, mu1-mu2=0), and in the symmetric case, storage
%effects in the lotery model actually don't opperate, and there is no coexistence. That sounds weird to me. Can we get some independent
%verification of that? Why would annual species be different in this respect? There must be some delta between 0.8 and 1 where \Delta^[EC]
%switches from positive to negative.

%***DAN: consider possile para on mu1-mu2=0 case
%***DAN: For discussion: is it true that ATA always weakens storage effects? Same as saying the ATA terms is always negative? The actual question is, for what models are ATA effects negative, versus positive?

@@

I think ata specialists are a thing - if their competitor is ubiquitous, they can only live in places on the landscape 
where there are atas. Could have a discussion para on it, if it does not make the results. Or both. BTW, ATA exclusion has a 
similar thing going on - a species excluded by ATAs (and competition) can only live on the portions of the landscape where
there are no ATAs. Could also describe the temporal way of it - the ATA specialist can only survive in a era/epoch for which there
are ATAs in its local, otherwise it'll have to go dormant or move elsewhere.
